---
title: "COVID_SCHOOL_DATA"
author: "James Hartner"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(janitor)
options(scipen=999)
library(tidycensus)
census_api_key("9f3430d359e022a7620289f71ec793ba915a884f")
```

## Including Plots

You can also embed plots, for example:

```{r}
covid_data<-read_csv("data/SchoolOutbreaks_cleanedv2.csv") 
update <-read_csv("data/Update_Oct_27_cleaned.csv")
testing<- read_csv("data/testing.csv")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
all_counties <- update%>%
  group_by(CountyReport)%>%
  summarize(
    total=sum(Number_of_Total_Cases)
  ) %>%
  arrange(desc(total))
print(all_counties)
```

This R piece has old data (before oct.27 update)
```{r}
list_of_counties <- covid_data %>%
  distinct(CountyReport) %>%
  arrange(CountyReport) %>%
  as_vector()
 
#list_of_counties <- list_of_counties[1]

for (county in list_of_counties) {
 # print(county)
  
  county_chart <- covid_data %>%
    filter(CountyReport==county) %>%
    group_by(School) %>%
    summarize(
      count=n(),
      total_cases=sum(Number_of_Total_Cases)
    ) %>%
    arrange(desc(total_cases)) %>%
    head(10) %>%
    ggplot() +
    geom_bar(aes(x=reorder(School,total_cases), weight=total_cases))+
    coord_flip() +
    labs(
      title= county,
      y = "Total Cases",
      x= "Schools"
    )  
  
  plot(county_chart)
    
}

```
```{r}

list_of_counties <- update %>%
  distinct(CountyReport) %>%
  arrange(CountyReport) %>%
  as_vector()
library('lubridate')

#list_of_dates <- update %>%
 # distinct(ReportDate) %>%
  #arrange(ReportDate) %>%
  #as_vector()

for (county in list_of_counties) {
  
  county_date<- update %>%
    mutate(ReportDate = mdy(ReportDate)) %>%
    filter(CountyReport==county) %>%
    group_by(ReportDate) %>%
    summarize(
      count=n(),
      total_cases=sum(Number_of_Total_Cases)
    ) %>%
    arrange(desc(total_cases)) %>%
    ggplot() +
    geom_line(aes(x=ReportDate, y=total_cases)) +
    #scale_x_date(date_breaks = "1 month", date_labels = "%m-%d-%y") +
    theme( 
      axis.text.x = element_text(angle = 45,  hjust=1)
      ) +
    labs(
        title= county,
        y = "Total Cases",
        x= "Schools"
      )
    
  
  plot(county_date)
    
}

```



```{r}
acs5 <-load_variables(2019, "acs5", cache = TRUE)
county_youth<- get_acs(geography = "county",
              variables = c(pop = "B06001_003"),
              state = "MD",
              year = 2019)%>%
          rename(CountyReport=NAME)%>%
          mutate(CountyReport = case_when(
    CountyReport == "Baltimore city, Maryland" ~ "Baltimore City",
    CountyReport == "Allegany County, Maryland" ~ "Allegany",
    CountyReport == "Anne Arundel County, Maryland" ~ "Anne Arundel",
    CountyReport == "Baltimore County, Maryland" ~ "Baltimore",
    CountyReport == "Calvert County, Maryland" ~ "Calvert",
    CountyReport == "Caroline County, Maryland" ~ "Caroline",
    CountyReport == "Carroll County, Maryland" ~ "Carroll",
    CountyReport == "Cecil County, Maryland" ~ "Cecil",
    CountyReport == "Charles County, Maryland" ~ "Charles",
    CountyReport == "Dorchester County, Maryland" ~ "Dorchester",
    CountyReport == "Frederick County, Maryland" ~ "Frederick",
    CountyReport == "Garrett County, Maryland" ~ "Garrett",
    CountyReport == "Harford County, Maryland" ~ "Harford",
    CountyReport == "Howard County, Maryland" ~ "Howard",
    CountyReport == "Kent County, Maryland" ~ "Kent",
    CountyReport == "Montgomery County, Maryland" ~ "Montgomery",
    CountyReport == "Prince George's County, Maryland" ~ "Prince George's",
    CountyReport == "Queen Anne's County, Maryland" ~ "Queen Anne's",
    CountyReport == "St. Mary's County, Maryland" ~ "St. Mary's",
    CountyReport == "Somerset County, Maryland" ~ "Somerset",
    CountyReport == "Talbot County, Maryland" ~ "Talbot",
    CountyReport == "Wicomico County, Maryland" ~ "Wicomico",
    CountyReport == "Worcester County, Maryland" ~ "Worcester",
    CountyReport == "Washington County, Maryland" ~ "Washington",
    TRUE ~ CountyReport
  ))
#joining

  
county_join<-county_youth %>%
  inner_join(all_counties, by=c("CountyReport"))%>%
  select(-moe,-variable,-GEOID)%>%
  rename(population=estimate)%>%
  mutate(
    per_100=(total/population)*100
  )%>%
  arrange(desc(per_100))

```
##TESTING (Data from Aug.1 to Nov.1)
```{r}
#Somerset Thoughts

Somerset_data <- testing %>%
  filter(CountyReport=="Somerset")
Baltimore_county_data <- testing %>%
  filter(CountyReport== "Baltimore") 
all_counties_testing<-testing %>%
  group_by(CountyReport)%>%
  summarize(
    total=sum(Number_of_Total_Cases)
  ) %>%
  arrange(desc(total)) %>%
print(all_counties)


county_join_test<-county_youth %>%
  inner_join(all_counties_testing, by=c("CountyReport"))%>%
  select(-moe,-variable,-GEOID)%>%
  rename(population=estimate)%>%
  mutate(
    per_100=(total/population)*100
  )%>%
  arrange(desc(per_100))
```
NOTES
#for (date in list_of_dates) {
 # print(county)
  
  date_report <- update %>%
    filter(ReportDate==date) %>%
    group_by(CountyReport) %>%
    summarize(
      count=n(),
      total_cases=sum(Number_of_Total_Cases)
    ) %>%
    arrange(desc(total_cases)) %>%
      ggplot() +
  geom_line(aes(x=date, y=total_cases)) +
   scale_x_date(date_breaks = "1 day", date_labels = "%m-%d-%y") +
   theme(
    axis.text.x = element_text(angle = 45,  hjust=1)
  ) +
   labs(
    title="fjdalfdsa",
    x = "Date",
    y = "Total Cases",
    caption = "source: Maryland.gov"
  ) +
  geom_point(aes(x=CountyReport, y=total_cases))
  
  plot(date_report)
}
list_of_dates <- update %>%
  distinct(ReportDate) %>%
  arrange(ReportDate) %>%
  as_vector()






